Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-19 talk_ucl_cdt_200622/introduction.tex
Intro slides

\begin{frame}
	\frametitle{Problem Description}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Data Generation}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Problem Description}
	Tritium breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
	\begin{center}
	$^1_0n + ^6_3Li \rightarrow ^3_1H + ^4_2He$ \hspace{20pt} $^1_0n + ^7_3Li \rightarrow ^3_1H + ^4_2He + ^1_0n$
	\end{center}
	However, the tritium breeding ratio (TBR) depends on numerous geometric and material parameters.\newline

	TBR evaluation \textit{Paramak} achieves very accurate results by OpenMC Monte Carlo neutronics simulation, but is computationally expensive.

	\vspace{15pt}

	\begin{center}
	    \textbf{Our Challenge:}
	\end{center}

	\begin{center}
	    \textbf{Produce a fast TBR function which strongly approximates Paramak, making use of the latest in surrogate modelling techniques.}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Data Generation}
	We designed the Approximate TBR Evaluator (ATE) package to generate training and test datasets from Paramak.\newline
	 \begin{columns}[onlytextwidth,T]
      \column{\dimexpr\linewidth-6cm-5mm}

        UCL's Hypatia cluster provided the multithreading power for us to produce one million TBR samples, representing 27 days of runtime.\newline

        These runs included full evaluations on the 18 continuous discrete parameters of Paramak, and "slice" evaluations with all discrete parameters frozen.

      \column{6cm}
      \vspace{0cm}
      \includegraphics[trim={0 0 0 2mm},clip,width=6cm]{params}

    \end{columns}
\end{frame}
